---
title: "UCP Leadership Scenarios"
author: "Alexander Ondrus"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Sankey Diagrams for UCP Leadership Scenarios

I found `@JLisaYoung`'s [tweet](https://twitter.com/JLisaYoung/status/1563956318687629313?s=20&t=dVd9B8BqAOqJe_76O1zKfQ) about potential outcomes of the UCP leadership race fascinating and so I wanted to contribute. Here's a brief overview of the steps that I undertook, along with the results.

### Data

I downloaded the data from the google sheet found [here](https://t.co/mYb79wLm5h) as an Excel workbook, removed all of the rows above the data on each sheet, tweaked the sheet names, and deleted the surprise plot twist (only because I didn't know how to visualize it, not because it didn't intrigue me).

For the "Base Model Declining Subsequent" sheet I deleted the "Adjusted Final" column as I wanted to be consistent with the prior columns in that sheet.

### Processing and Visualizing

I wrote functions in R to read in the data and visualize it using David Sjoberg's `ggsankey` package (see [here](https://github.com/davidsjoberg/ggsankey)) for details. The functions I worte are contained in the `HelperFunctions.R` file in my [GitHub repo](https://github.com/alex-ondrus/ucp-leadership-sankeys) for this project.

### Results

Here are the Sankeys that were obtained for each of the different scenarios listed:

```{r generate-sankeys, message=FALSE, warning=FALSE, results='asis'}
source('HelperFunctions.R')

sheet_names <- excel_sheets("UCP Leadership Scenarios.xlsx")

sankeys_list <- list()

for(current_sheet_name in sheet_names){
  sankeys_list[[current_sheet_name]] <- knitr::knit_child(
    "IndividualSankey.rmd",
    envir = environment(),
    quiet = TRUE
  )
}

cat(unlist(sankeys_list), sep = "\n")
```

